\documentclass[a4paper,10pt]{letter}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{charter}
\usepackage{parskip}
\geometry{margin=1in}
\hypersetup{
	colorlinks=true,
	urlcolor=black,
	linkcolor=black
}
\setstretch{1.1}


\longindentation=0pt
\signature{\vspace{-2.2em} Max Sherman}
\address{Nijmegen, The Netherlands \\ \href{mailto:work.maxsherman@outlook.com}{work.maxsherman@outlook.com} \\ +44 (0) 7944 304 575 \\ \href{https://maxsherman.vercel.app}{maxsherman.vercel.app}}
\date{\today}

\makeatletter
\let\@texttop\relax
\makeatother

\begin{document}
	
	\begin{letter}{Hiring Team \\ McLaren Automotive \\ Chertsey Road \\ Woking, Surrey \\ GU21 4YH \\ United Kingdom}
		
		\opening{Dear Hiring Team,}
		
		I am writing to apply for IT Graduate Scheme at McLaren Automotive. With a First-Class Bachelor in Computer Science, experience as a software engineering undergraduate at Jaguar Land Rover, and a strong technical background in data engineering, AI, embedded systems, and full-stack development, I am eager to contribute to McLaren's mission of building the world's most desirable luxury performance vehicles.
		
		During my placement at Jaguar Land Rover, I developed and optimised AUTOSAR-compliant Simulink models for control systems, improving model efficiency and maintainability by over 60\%. Demonstrating initiative and a strong capacity for rapid learning, I was promoted to Function Owner within six months, leading a small team to develop, calibrate, and validate embedded control software. This experience deepened my understanding of automotive software development and its complexities, whilst further fuelling my curiosity for cutting-edge automotive innovation. 
		
		Beyond my technical contributions, I actively sought opportunities to challenge myself and support others. As a team lead in the DRIVEN project, an early-careers initiative at JLR, I oversaw the design, development, testing, and integration of software for a Greenpower Formula 24 racecar. I implemented industry-standard practices such as Agile methodology, JIRA, and GitLab, and was recognised with two "Amped-Up" awards for exceptional leadership and dedication. Through this role, I strengthened my leadership and accountability skills, promoting open collaboration and feedback whilst consistently delivering results under tight deadlines. 
		
		My academic background complements this practical experience. I have built a strong foundation in software engineering and data science, achieving a first-class GPA of 80\%. My final-year project, an F1 Data Analysis Tool built in Python, reflects my long-standing passion for motorsport and innovation through software. Furthermore, my interest in AI-driven analytics and predictive modelling in motorsports led me to develop a PySpark-based data mining project where I explored race performance patterns.
		
		
		McLaren's core values of innovation, high performance, and teamwork, resonate deeply with my approach to engineering and collaboration. The rotational nature of this programme especially appeals to me, as it provides the ideal environment to learn, grow, and contribute across areas such as cybersecurity, AI, and data engineering. I am eager to develop my skills within your IT organisation and contribute to smarter, faster, and more robust digital solutions. 
		
		I would be honoured to bring my technical skills, problem-solving ability, and enthusiasm for automotive innovation to McLaren Automotive. Thank you for considering my application.
		
		\vspace{1em}
		
		\closing{Yours sincerely,}
		
	\end{letter}
	
\end{document}
