\documentclass[a4paper,10pt]{letter}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{charter}
\usepackage{parskip}
\geometry{margin=1in}
\hypersetup{
	colorlinks=true,
	urlcolor=black,
	linkcolor=black
}
\setstretch{1.1}


\longindentation=0pt
\signature{\vspace{-2.2em} Max Sherman}
\address{Nijmegen, The Netherlands \\ \href{mailto:work.maxsherman@outlook.com}{work.maxsherman@outlook.com} \\ +44 (0) 7944 304 575 \\ \href{https://maxsherman.vercel.app}{maxsherman.vercel.app}}
\date{\today}

\makeatletter
\let\@texttop\relax
\makeatother

\begin{document}
	
	\begin{letter}{Hiring Team \\ Mercedes-AMG High Performance Powertrains \\ Morgan Drive \\ Brixworth, Northamptonshire, \\ NN6 9GZ \\ United Kingdom}
		
		\opening{Dear Hiring Team,}
		
		I am writing to apply for the Software and Controls Graduate position at Mercedes-AMG HPP. The opportunity to contribute to world-leading power unit development, collaborate with exceptional engineers, and rotate across departments including control systems, testing, mechatronics, and advanced technologies is precisely the environment in which I want to grow. Mercedes-AMG HPP's culture of innovation, precision, and continuous improvement reflects the standards I set for myself.		
		
		During my year-long placement with Jaguar Land Rover, I developed and optimised AUTOSAR-compliant Simulink models for control systems, improving model efficiency and maintainability by over 60\%. Demonstrating initiative and a strong capacity for rapid learning, I was promoted to Function Owner within six months, leading a small team to develop, calibrate, and validate embedded software.
		
		Beyond my technical contributions, I actively sought opportunities to challenge myself and support others. As a team lead in the DRIVEN project, an early-careers initiative at JLR, I oversaw the design, development, testing, and integration of control software for a Greenpower Formula 24 racecar. I implemented industry-standard practices such as Agile methodology, JIRA, and CI/CD, and was recognised with two "Amped-Up" awards for exceptional leadership and dedication.
		
		My academic background complements this practical experience. I hold a Bachelor of Science with First-Class Honours in Computer Science from the University of Brighton. I have built a strong foundation in software engineering and data science, achieving a first-class GPA of 80\%. I chose to study computing due to my passion for problem-solving, mathematics, and technological innovation. I have always been driven by a desire to understand how complex systems work and computer science offered the perfect combination of theory, creativity, and practical application.
		
		For my final-year project, I developed a telemetry visualisation and statistical analysis tool built in Python, which was designed to provide actionable insights from complex F1 data. The project covered the complete development process, from architectural design and requirements gathering to testing and evaluation. I developed a scalable data pipeline, advanced statistical analysis modules, and interactive visualisations, which were integrated into an intuitive user interface. The project received 85\% for the report and 95\% for the presentation, and reflects my long-standing passion for motorsport and innovation through software. 
		
		I would be honoured to bring my technical skills, enthusiasm, and commitment to excellence to Mercedes-AMG HPP. Thank you for considering my application.
		
		\vspace{1em}
		
		\closing{Yours sincerely,}
		
	\end{letter}
	
\end{document}
